Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-01-11 paperIEEE.tex
Some Introduction
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@72 db7c848b-7755-4df2-b763-8796797afa52

\author{Stefan~Eilemann, David~Steiner and Renato Pajarola%
\IEEEcompsocitemizethanks{\IEEEcompsocthanksitem All authors are with the
Visualization and MultiMedia Lab, Department of Informatics, University of
Z\"urich.
\IEEEcompsocthanksitem S. Eilemann is also with the Blue Brain Project, Ecole
Polytechnique Federale de Lausanne.}}

@@

@@

Subpixel compounds (\fig{fig:subpixel}) are similar to pixel compounds, but they
decompose the work for a single pixel, for example when using FSAA or depth of
field. Composition typically uses accumulation and averaging of all computed
fragments for a pixel. This feature is not fully transparent to the application,
since it needs to adapt (jitter or tilt) the frustum based on the iteration
executed. Furthermore, subpixel compounds interact with idle image refinements,
e.g., they can accelerate idle anti-aliasing of a scene when the camera and
scene are not changed.

@@

RTT Scale uses a master-slave execution mode, were a single running Deltagen
instance can go into ``Scale mode'' at any time by launching an
\textsf{Equalizer}
configuration. Consequently, the whole internal representation needed for
rendering is based on a \textsf{Collage}-based data distribution. The rendering
clients
are separate, smaller applications which will map their scenes during
startup. At runtime, any change performed in the main application is committed
as a delta at the beginning of the next frame, following a design pattern
similar to the \textsf{Collage} \textsf{Serializable}
(\sref{sec:Serializable}). Multicast (\sref{sec:RSP}) is used to keep data
distribution times during session launch reasonable for larger cluster sizes
(tens to hundreds of nodes).

RTT Scale is used for a wide variety of use cases. In virtual reality, the
application is used for virtual prototyping and design reviews in front of
high-resolution display walls or in a CAVE and for virtual prototyping of
human-machine interactions in a CAVE or using HMDs. For scalability, sort-first
and tile compounds are used to achieve fast, high-quality rendering, primarily
for interactive raytracing, both based on CPUs and GPUs. For CPU-based
raytracing, often Linux-based rendering clients are used with a Windows-based
application node.

>>>>

\author{Stefan~Eilemann, David~Steiner and Renato Pajarola%
\IEEEcompsocitemizethanks{All authors are with the
Visualization and MultiMedia Lab, Department of Informatics, University of
Z\"urich.}}

@@

In this systems paper, we present an overview of the integration of research and
commercial developments into the Equalizer parallel rendering framework first
presented in \cite{EMP:09}. While individual research using the system has been
presented since, many important features have not previously been published and
are presented here. In particular, the integration of parallel rendering
research, APIs for developing complex distributed applications, and many
individual features make Equalizer an unique, open source framework to develop
visualization applications for any type of setup and use case.

@@

Subpixel compounds (\fig{fig:subpixel}) are similar to pixel compounds, but they
decompose the work for a single pixel, for example with Monte-Carlo ray tracing,
FSAA or depth of field rendering. Composition typically uses accumulation and
averaging of all computed fragments for a pixel. This feature is not fully
transparent to the application, since it needs to adapt (jitter or tilt) the
frustum based on the iteration executed. Furthermore, subpixel compounds
interact with idle image refinements, e.g., they can accelerate idle
anti-aliasing of a scene when the camera and scene are not changed.

@@

RTT Scale uses a master-slave execution mode, were a single running Deltagen
instance can go into ``Scale mode'' at any time by launching an
\textsf{Equalizer} configuration. Consequently, the whole internal
representation needed for rendering is based on a \textsf{Collage}-based data
distribution. The rendering clients are separate, smaller applications which
will map their scenes during startup. At runtime, any change performed in the
main application is committed as a delta at the beginning of the next frame,
following a design pattern similar to the \textsf{Collage Serializable}
(\sref{sec:Serializable}). Multicast (\sref{sec:RSP}) is used to keep data
distribution times during session launch reasonable for larger cluster sizes
(tens to hundreds of nodes).

RTT Scale is used for a wide variety of use cases. In virtual reality, the
application is used for virtual prototyping and design reviews in front of
high-resolution display walls and CAVEs, as well as for virtual prototyping of
human-machine interactions CAVEs and HMDs (\fig{FIG_teaser}(b)). For
scalability, sort-first and tile compounds are used to achieve fast,
high-quality rendering, primarily for interactive raytracing, both based on CPUs
and GPUs. For CPU-based raytracing, often Linux-based rendering clients are used
with a Windows-based application node.
